# Getting started with Synapse using R

Import the synapse R client and log in to Synapse using locally stored credentials. New users have to supply username and password or their Synapse session API key but can stash these using 

synapseLogin(<username>, <password>, rememberbe=T)

```{r}
library(synapseClient)
synapseLogin()

RESULT_FOLDER = 'syn6134567'
DATA_FILE = 'syn6115761'
```


#### Fetch the dataset for Problem 2 and read into data frame
```{r}
dataFile <- synGet(DATA_FILE)
df <- read.delim(dataFile@filePath, header=T, sep=',')
```

#### Visualize correlation structure between certain variables
```{r}
df_small <- df[c('GAGEBRTH', 'BIRTHWT','BIRTHLEN', 'BIRTHHC', 'HAZ', 'WHZ', 'BAZ')]
png(file="demo_plot.png")
pairs(df_small)
dev.off()

plotFileEntity <- File(path="demo_plot.png", parentId=RESULT_FOLDER)
plotFileEntity <- synStore(plotFileEntity, 
                           used=dataFile, 
                           executed='https://github.com/Sage-Bionetworks/HBGDki_Hackathon/blob/master/Synapse_R_API_demo.Rmd')
```


#### See content in Synapse
```{r}
onWeb(plotFileEntity)
```

